Supporting Information

### 2015-09-01 si.Rmd
re-arranged supp figs and tables. removed nasty in situ figure from ms
started code for sf_isGenesTpm

@@

labels <- c("1" = "Detected\nin both", "2" = "Only detected\nby in situ", "3" = "Only detected by\nRNA-sequencing")

>>>>

```{r sf_isGenesTpm, fig.height = 14}
print(sf_isGenesTpm)
```

**`r I(pasteLabel("Figure S", s_figCount, "sf_isGenesTpm"))`**: Expression patterns of genes compared to *in situ* results.

@@
